IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-01-31 codes/R/cohorts_nc.Rnw
- fix LOESS on income - add table with mean factors

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\subsection{Inequality in noncognitive ability}
The model can be used to investigate how inequality of noncognitive skills has changed between the two cohorts. The variances of the $EXT$ and $INT$ factors are estimated to be larger in the MCS children by \Sexpr{round(lv.covs$MCS[1,1]-1,2)} and \Sexpr{round(lv.covs$MCS[2,2]-1,2)} of a standard deviation, respectively, indicating larger dispersion.

@@

@@

\begin{figure}
<<FACLOESS_INC, dev='tikz', fig.height=5, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Scores and family income}
{\scriptsize \emph{Notes}: The figure plots LOESS of the scored factors against family income. \par}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\subsection{Inequality in noncognitive ability}
The model can be used to investigate how inequality of noncognitive skills has changed between the two cohorts. 
%The variances of the $EXT$ and $INT$ factors are estimated to be larger in the MCS children by \Sexpr{round(lv.covs$MCS[1,1]-1,2)} and \Sexpr{round(lv.covs$MCS[2,2]-1,2)} of a standard deviation, respectively, indicating larger dispersion.

@@

\begin{table}[ht]
\caption{Estimated latent variable means and covariances} \label{tab:lvpars}
\centering
<<FA_COMP, dependson='FA_SCORES', results='asis'>>=
# compare mean factor scores by gender and cohort

prn <- function(obj) sprintf("%.3f", round(obj,3))

sctable <- aggregate(items.scored[[4]][, c("EXT", "INT", "EXT.RAW", "INT.RAW")], list(items.scored[[4]]$cohortsex), 
                   FUN = function (x) c(mn = prn(mean(x)), med = prn(median(x))))
sctable <- cbind(group = factor(c(1,3,2,4)), sctable)
levels(sctable$group) <- c("BCS Males", "MCS Males", "BCS Females", "MCS Females")
sctable <- sctable[order(sctable$group),]
sctable <- sctable[, !names(sctable) %in% "Group.1"]
sctable <- as.matrix(sctable,3)

print.xtable(xtable(sctable,
                    align="L{0cm}L{2.2cm}C{1.3cm}C{1.3cm}C{1.3cm}C{1.3cm}C{1.3cm}C{1.3cm}C{1.3cm}C{1.3cm}",
                    digits = 3
                    ),
             size="\\small",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0,4)),
                              command = c(
                              # header
                                   "\\toprule
                                    & \\multicolumn{4}{c}{\\textbf{Scored factors}}
                                    & \\multicolumn{4}{c}{\\textbf{Scales}} \\\\ \\cmidrule(lr){2-5} \\cmidrule(lr){6-9}
                                    & \\multicolumn{2}{c}{EXT} & \\multicolumn{2}{c}{INT} & \\multicolumn{2}{c}{EXT} & \\multicolumn{2}{c}{INT} \\\\ \\cmidrule(lr){2-3} \\cmidrule(lr){4-5} \\cmidrule(lr){6-7} \\cmidrule(lr){8-9}
                      & Mean & Median & Mean & Median & Mean & Median & Mean & Median \\\\",
                      "\\bottomrule"
                                    )),
             hline.after = NULL,  # remove default booktabs lines
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabularx", width = "\\textwidth",
             floating = FALSE
)

@@

\begin{figure}
<<FACLOESS_INC, dev='tikz', fig.height=10, fig.width=10, out.width='1\\linewidth'>>=
@
\caption{Scores and family income}
{\scriptsize \emph{Notes}: The figure plots LOESS of the scored factors against family income. \par}
\end{figure}
